---
title: 'Computer Assignment 2: France (Group 12)'
author: "Javier Torralba Flores (ANR: u146430, SNR: 2042878), Maximilian Grotz (ANR:
  u271366, SNR: 2056313), Abdirahman Nuur (ANR: u824009 , SNR: 2057152) and Mathieu
  Van de Vel (ANR: u130770, SNR: 2050053)"
date: "14/04/2021"
output:
  html_notebook: default
---

# Q1: Data preperation

```{r}
library(readxl)
library(dplyr)
library(tidyverse)
library(lubridate) # This package is used for working with dates

options(scipen = 99999)

# Importing the Current Account Balance as a % of GDP of France

CABalance_FR <- read_csv("sourcecode/FRED_bop_france_quarterly.csv", 
    col_types = cols(DATE = col_date(format = "%d/%m/%Y"), 
        FRAB6BLTT02STSAQ = col_number())) %>%
  rename(date = DATE, CAasPercGDP_quart_FR = FRAB6BLTT02STSAQ)


# Importing the General Government Debt as a % of GDP. THIS IS NOT IN PERCENT! GOVERNMENT DEBT OF 100%  = 1

GovDebt_FR <- read_csv("sourcecode/OECD_gov_debt_annual.csv", 
    col_types = cols(LOCATION = col_character(), 
        INDICATOR = col_skip(), SUBJECT = col_skip(), 
        MEASURE = col_skip(), FREQUENCY = col_skip(), 
        TIME = col_date(format = "%Y"), Value = col_number(), 
        `Flag Codes` = col_skip())) %>%
  rename(date = TIME) %>%
  filter(LOCATION == "FRA") %>%
  mutate(LOCATION = NULL, GovDebt_ann_FR = Value / 100, Value = NULL)


# Importing Interest Rate on Government Bonds (10 year), also called "Long term interest rate", in %/annum

# This function transform dates in a quarterly format of "2000-Q1" to 2000-01-01
QuarterToDate <- function(QuarterlyDate){
  
  NumberofQuarter <- substr(QuarterlyDate, 7, 7)
  
  Month <- 3 * as.numeric(NumberofQuarter) - 2
  Month <- ifelse(Month == 10, Month, paste(0, Month))
  
  Year <- substr(QuarterlyDate ,1, 4)
  
  Date_String <- paste(Year, "-", Month, "-01") %>%
    str_replace_all(" ", "")
  
  Date <- as.Date(Date_String)
  
  Date
}

IntRate_FR <- read_csv("sourcecode/OECD_interest_rates_france_quarterly.csv", 
    col_types = cols(INDICATOR = col_skip(), 
        SUBJECT = col_skip(), MEASURE = col_skip(), 
        FREQUENCY = col_skip(), Value = col_number(), 
        `Flag Codes` = col_skip())) %>%
  mutate(date = QuarterToDate(TIME), IntRate_quart_FR = Value / 100, Value = NULL, TIME = NULL, LOCATION = NULL)


# Exchange rate against the US dollar

XR_EurUSD <- read_csv("sourcecode/FRED_exchage_rate_quarterly.csv", 
    col_types = cols(DATE = col_date(format = "%d/%m/%Y"), 
        DEXUSEU = col_number())) %>%
  rename(date = DATE, XR_quart_EurUSD = DEXUSEU) %>%
  mutate(XR_quart_EurUSD = 1/XR_quart_EurUSD)


# Total GDP, in millions of US dollars

GDP_FR <- read_csv("sourcecode/FRED_euros_france_gdp_quarterly.csv", 
    col_types = cols(DATE = col_date(format = "%d/%m/%Y"), 
        CPMNACSCAB1GQFR = col_number())) %>%
  mutate(date = DATE, DATE = NULL, GDP_quart_USD_FR = CPMNACSCAB1GQFR * 1000000 / 0.8385451, CPMNACSCAB1GQFR = NULL)


# Investment (usually Gross Fixed Capital Formation), in millions of US dollars

Invest_FR <- read_csv("sourcecode/FRED_euros_investments_quarterly.csv", 
    col_types = cols(DATE = col_date(format = "%d/%m/%Y"), 
        FRAGFCFQDSMEI = col_number())) %>%
  mutate(Invest_quart_USD_FR = FRAGFCFQDSMEI / 0.8385451, FRAGFCFQDSMEI = NULL) %>%
  rename(date = DATE)


# Gross national savings as a % of GDP (savings rate). Again, this is in decimals, and not percent

SavingsR_FR <- read_csv("sourcecode/OECD_savings_rate_annual.csv", 
    col_types = cols(INDICATOR = col_skip(), 
        SUBJECT = col_skip(), MEASURE = col_skip(), 
        FREQUENCY = col_skip(), TIME = col_date(format = "%Y"), 
        Value = col_number(), `Flag Codes` = col_skip())) %>%
  filter(LOCATION == "FRA") %>%
  mutate(SavR_ann_FR = Value / 100, LOCATION = NULL, Value = NULL) %>%
  rename(date = TIME)


# Merging them all together

DF_FR <- CABalance_FR %>%
  full_join(IntRate_FR, by = "date") %>%
  full_join(XR_EurUSD, by = "date") %>%
  full_join(GDP_FR, by = "date") %>%
  full_join(Invest_FR, by = "date") %>%
  full_join(GovDebt_FR, by = "date") %>%
  full_join(SavingsR_FR, by = "date") %>%
  filter(date != "1998-10-01")

DF_quart_FR <- DF_FR %>%
  select(!c(GovDebt_ann_FR, SavR_ann_FR))

DF_ann_FR <- DF_FR %>%
  select(c(date, GovDebt_ann_FR, SavR_ann_FR)) %>%
  na.omit()

print(DF_quart_FR)

print(DF_ann_FR)

```


# Q2: Government debt, interest rate, current account and the exchange rate

## 1. Government debt and interest rate

```{r}


```



## 2. Current account and the exchange rate

```{r}


```



## 3. Relevant events and policy responses



## 4. Currency union and its effects



# Q3: Investment rate and the Feldstein-Horioka puzzle

## 1. Investment rate


## 2. Investment rate: Graph

```{r}


```


## 3. Feldstein-Horioka puzzle


# References
